Do We Judge Children's Books by Their Covers? 

### 2024-12-04 paper/paper.qmd
Re-render paper for the fix in model, improved measurement section, fix label caption

This paper aims to use simple linear regression models and fine-tuned pretrained transformer models, by analyzing children's book data from Goodreads[@goodreaddata1;@goodreaddata2], to uncover how much such first impression will influence the rating of a book. The study provides guidance for author and publishers to create attractive titles, identifies traits in children's book rating, which may be useful for designing recommendation systems. Where these recommendation systems, when it comes to children, may be difficult to create due to lack of user generated data, and will likely benefit from understanding provided by this study.

@@

## Data Measurement
Goodreads is an American book recommendation and social networking platform. Its primary purpose is to allow users to catalog their books, keep track of their reading progress, share reviews, and engage in discussions about literature. The included books are mainly in English, with some books in other languages available. Any registered user on Goodreads may give rating to any book, the rating comes in integers from 1 to 5, with no half-star option. Along with a rating, user also may write text reviews for the book, which may be seen by other users.

@@

```{r}
#| label: fig-ratingoverview
#| fig-cap: Histogram on average rating
#| include: true
#| echo: false
#| warning: false
#| message: false

ggplot(book_data, aes(x = as.numeric(average_rating))) + 
  geom_histogram(binwidth = 0.1, fill = "skyblue", color = "black", alpha = 0.7) +
  labs(
    title = "Histogram of Average Ratings",
    x = "Average Rating",
    y = "Count(Books)"
  ) +
  theme_minimal()
```

@@

```{r}
#| label: fig-textreview
#| fig-cap: Histogram on Number of Text Review
#| include: true
#| echo: false
#| warning: false
#| message: false

ggplot(book_data, aes(x = as.numeric(text_reviews_count))) + 
  geom_histogram(binwidth = 0.1, fill = "skyblue", color = "black", alpha = 0.3) +
  labs(
    title = "Histogram of Number of Text Review",
    x = "Number of Text Review",
    y = "Books(Log Scale)"
  ) + 
  xlim(0, 1000) +  # Set x-axis limit 
  scale_y_log10()+  # Set y-axis to log scale
  theme_minimal()
```

@@

```{r}
#| label: fig-textreviewratio
#| fig-cap: Histogram on Ratio of Text Review
#| include: true
#| echo: false
#| warning: false
#| message: false

@@

```{r}
#| label: fig-num_pages_overview
#| fig-cap: Histogram on Ratio of Text Review
#| include: true
#| echo: false
#| warning: false
#| message: false

@@

#### Text Reviews Ratio
For each 1% increase in the ratio of text reviews to total reviews, the average rating increases by 0.0763.
This is one of the most influential variables in the model. Books that have a higher ratio of text reviews and more detailed feedback from readers tend to receive significantly higher ratings. Indicating that detailed text-based reviews are more strongly associated with higher ratings than numerical ratings. We could also explain association by the positive impression created through higher engagement.

>>>>

The estimand of this study is the level of reader satisfaction with a book, as reflected by its average rating. Specifically, this paper aims to determine the extent to which first impressions influence overall satisfaction.

This paper made use of simple linear regression models and fine-tuned pretrained transformer models, by analyzing children's book data from Goodreads[@goodreaddata1;@goodreaddata2], to uncover how much such first impression will influence the rating of a book. The study provides guidance for author and publishers to create attractive titles, identifies traits in children's book rating, which may be useful for designing recommendation systems. Where these recommendation systems, when it comes to children, may be difficult to create due to lack of user generated data, and will likely benefit from understanding provided by this study.

@@

## Data Measurement
Goodreads is an American book recommendation and social networking platform. Its primary purpose is to allow users to catalog their books, keep track of their reading progress, share reviews, and engage in discussions about literature. The included books are mainly in English, with some books in other languages available. Any registered user on Goodreads may give rating to any book, the rating comes in integers from 1 to 5, with no half-star option. Along with a rating, user also may write text reviews for the book, which may be seen by other users. Descriptions of a book were updated by volunteer and staffs that maintains the website, while the rating contents are user generated.

One issue this may raise is as each user has different understand of rating, the aggregate effect may lower the effectiveness of rating's role as a estimand for satisfaction.

@@

```{r}
#| label: fig-ratingoverview
#| fig-cap: Distribution of average rating
#| include: true
#| echo: false
#| warning: false
#| message: false

ggplot(book_data, aes(x = as.numeric(average_rating))) + 
  geom_histogram(binwidth = 0.1, fill = "skyblue", color = "black", alpha = 0.7) +
  labs(
    x = "Average Rating",
    y = "Count(Books)"
  ) +
  theme_minimal()
```

@@

```{r}
#| label: fig-textreview
#| fig-cap: Distribution of Number of Text Review
#| include: true
#| echo: false
#| warning: false
#| message: false

ggplot(book_data, aes(x = as.numeric(text_reviews_count))) + 
  geom_histogram(binwidth = 0.1, fill = "skyblue", color = "black", alpha = 0.3) +
  labs(
    x = "Number of Text Review",
    y = "Books(Log Scale)"
  ) + 
  xlim(0, 1000) +  # Set x-axis limit 
  scale_y_log10()+  # Set y-axis to log scale
  theme_minimal()
```

@@

```{r}
#| label: fig-textreviewratio
#| fig-cap: Dirtribution of the Ratio of Text Review
#| include: true
#| echo: false
#| warning: false
#| message: false

@@

```{r}
#| label: fig-num_pages_overview
#| fig-cap: Distribution of number of pages
#| include: true
#| echo: false
#| warning: false
#| message: false

@@

#### Text Reviews Ratio
For each 1% increase in the ratio of text reviews to total reviews, the average rating increases by 0.0801.
This is one of the most influential variables in the model. Books that have a higher ratio of text reviews and more detailed feedback from readers tend to receive significantly higher ratings. Indicating that detailed text-based reviews are more strongly associated with higher ratings than numerical ratings. We could also explain association by the positive impression created through higher engagement.
